---
title: "demo"
author: "Keach Murakami"
output: md_document
# output: html_document
---

```{r setup, warning = F, message = F}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, cache = T, out.width = "50%")
# load core functions and libraries
library(dualband)
library(imager)
library(EBImage)
library(pri)
set_read_img("jpg")
```

# Demo

## Load images

```{r load_images}
(img_files <- dir("sample_data/", full.names = T))

img_demo <-
  img_files %>%
  read_imgs %>%
  .^3 # correct gamma value

dualband::show(img_demo, browser = F, all = F)
```

## Divide images into small pieces

To divide images, the locations should be approximated.

```{r set_locations}
location_demo <-
  tribble(
     ~ x,  ~ y, ~ size, ~ location,
     474,  501,    100,    "a",
    1497,  933,    100,    "b"
  )
location_demo
```

The images are divided into a list of small images---called pieces.

```{r split_into_pieces}
piece_demo <-
  location_demo %>%
  split(.$location) %>%
  map(~ divide_piece(., img_demo))

piece_demo %>%
  map(dualband::show, browser = F)
```


## Detect markers

Determine a center of the marker with `set_center`.
A binarised piece can be checked as the side-effect (`.check = T`).
This function appends attributes related to binarisation, eroding, and geomery of white-reflectance to the input image.
That is, only attributes will be changed.
Returns `NULL` when the `.check = T`.

```{r set_center, message = F}
piece_demo %>%
  map(~ set_center(., .check = T, browser = F,
                   white_ratio = .95, erode_size = 1, occupancy = .001))

piece_demo_1 <-
  piece_demo %>%
  map(~ set_center(., .check = F, browser = F,
                   white_ratio = .95, erode_size = 1, occupancy = .001))

```

- white_ratio (0--1)
    - bright pixels within top `X%` are regarded as the white regions.
- erode_size (int)
    - if the white regions are separated, the regions may be merged by increasing this factor.
- occupancy (0--1)
    - smaller regions can be removed by increasing this factor although the smaller regions do not count as long as a true white region is the largest.
  
  
## Set ROIs

Determine the ROIs with `set_masks`.
A masked piece can be checked as the side-effect (`.check = T`).
This function appends attributes related to ROIS to the input image.
That is, only attributes will be changed.
Returns `NULL` when the `.check = T`.

```{r set_rois}
piece_demo_1 %>%
  map(~ set_masks(., .check = T, browser = F,
                  ref_white_ratio = 1/5, margin_white_ratio = 1.2, outer_white_ratio = 2))

piece_demo_2 <-
  piece_demo_1 %>%
  map(~ set_masks(., .check = F, browser = F,
                  ref_white_ratio = 1/5, margin_white_ratio = 1.2, outer_white_ratio = 2))
```

```{r geometry}

sizes <-
  c(ref = .5, white = 1, margin = 1.2, outer = 2)
colors <-
  c(ref = "grey50", white = "white", margin = "black", outer = "orange")

rectangles <-
  map2(rev(sizes), rev(colors),
       ~ annotate(geom = "rect", xmin = -.x, xmax = .x, ymin = -.x, ymax = .x, fill = .y))

tibble() %>%
  ggplot(aes()) +
  theme_minimal() +
  rectangles +
  coord_fixed()
```

- ref_white_ratio (0--1)
    - grey / white
- margin_white_ratio ( > 1)
    - black / white
- outer_white_ratio ( > margin_white_ratio)
    - orange / white

## Summarise marker data

Statistics can be summarised by `extract_reflectance`.

```{r summarise}
piece_demo_2 %>%
  map(extract_reflectance)
```


## Check mapping

Map reference (i.e. reflectance standard) and target (i.e. leaf) regions on the input image.

```{r mapping}
masked_pieces_demo <-
  piece_demo_2 %>%
  # adjust mapping colors and pixel values
  map(check_mask, map_rgb = c(marker = 1, target = 3), map_int = c(marker = 10, target = 10))

masked_full_demo <-
  map_full(list_pieces = masked_pieces_demo, full_size_img = img_demo)

dualband::show(masked_full_demo, browser = F)
```


# Session information

```{r session_info}
devtools::session_info()
```
